---
title: "My First Exercise"
author: "Warren Liu"
date: "May 7th 2020"
output: 
  pdf_document:
    toc: true
    toc_depth: 2
---
# NSFW Posts? Ooh, getting saucy here aren't we?
Firstly, let's explore the relation between Whether a Post is marked Over 18 and the amount of points it receives
```{r}
library(tidyverse)
library(ggplot2)

data_df <- read.csv("r_dataisbeautiful_posts.csv")

boxplot(score ~ over_18 , data= data_df, main="Distribution of scores, by whether a post is NSFW",
   xlab="NSFW or Not?", ylab="Score")
```
As we see, the IQR is quite similar, and there are a lot of outliers. However, it seems that non NSFW posts generally garnish more points.

Well, data isn't always beautiful;

# Scores vs Awards Received
Why don't we see how generous our community is?

```{r}
library(ggplot2)
ggplot(data_df, aes(x=score, y=total_awards_received)) + geom_point(size=0.5)

```

Well crap. It seems like people generally don't give many awards on reddit.

What is another thing we could potentially explore?

```{r}
library(ggplot2)
ggplot(data_df, aes(x=num_comments, y=score)) + geom_point(size=0.5) + geom_smooth(method=lm, se=FALSE)

```

Bah, still Inconclusive (at least the relationship isn't independent). Why don't we try another type of graph?
```{r}
p <- ggplot(data_df, aes(x=num_comments)) +
  geom_density()
print(p)
```
Well damn, that was way too big. It almost looks like the axis. Thus, lets perform some calculations and eliminate all the outliers.

```{r}
data_num_comm = data_df$num_comments

summary(data_num_comm)

```

Okay, this means that the limit for outliers is Q3 + 1.5IQR should be 8.5 or 8 comments. This suggests that most posts tend to generally Die in NEW, and Reddit's algorithm tends to promote only a select few posts to be trending. For the sake of data, i'll expand it to 150 comments. This shows a distinct left skew.

```{r}
ggplot(data_df, aes(x=num_comments)) +
  geom_density(color="darkblue", fill="lightblue") + coord_cartesian(xlim = c(0,   150))

```

Now Let us Filter out some undesirable Variables. We'll filter out the no awards, and ensure that the score is at least 100.
```{r}
library(ggplot2)

filt_df <- data_df %>% filter(
  100 < score,  total_awards_received > 0
  )

ggplot(filt_df, aes(x=score, y=num_comments)) + geom_point(size=0.5) + geom_smooth(method=lm)


```
Welp, Guess I'll stick to matplotlib and python.